### 2012-11-05 poster/poster.tex
Prescreened poster
Final poster, printed

\definecolor{lightorange}{rgb}{0.9,0.4,0}
\definecolor{lightestorange}{rgb}{1,0.8,0.5}
\definecolor{darkorange}{rgb}{0.2,0.1,0}
\definecolor{ForestGreen}{rgb}{0.13, 0.54, 0.13}
\definecolor{navyblue}{rgb}{0,0,0.5}
%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lightestorange,
  bgColorTwo=white,
  borderColor=darkorange,
  headerColorOne=ForestGreen,
  headerColorTwo=navyblue,
  headerFontColor=white,
  boxColorOne=green,
  boxColorTwo=blue,
  columns=3,
  % Format of textbox
  textborder=faded,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.1\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=none,
  linewidth=2pt
  }
  % Eye Catcher
  {\includegraphics[height=7em]{images/clojure-logo10.png}} 
  % Title
  {\bf\textsc{A Practical Optional Type System for Clojure}}
  % Authors
  %{\textsc{\{ Brian.Amberg and Thomas.Vetter \}@unibas.ch}}
  { \textsc{Ambrose Bonnaire-Sergeant <abonnairesergeant@gmail.com>}
    \\
    \textsc{{Supervised by Rowan Davies <rowan@csse.uwa.edu.au>}}}
  % University logo
  {% The makebox allows the title to flow into the logo, this is a hack because of the L shaped logo.
    \includegraphics[height=6.0em]{images/1000px-UWA_crest.png}
  }
%
%  % Eye Catcher
%  {\includegraphics{images/1000px-UWA_crest}}
%   
%  % Title
%  { \textsc}
%  % Authors
%  % University logo
%  { University of Western Australia }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position 
%%% towards an already declared box. So if you have a box attached to the 
%%% bottom, one to the top and a third one which should be in between, you 
%%% have to specify the top and bottom boxes before you specify the middle 
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We take the lessons learnt from several projects to design \emph{Typed Clojure},
an optional type system for Clojure running on the Java Virtual Machine. 
The main contributions are:
\begin{itemize}
  \item We develop a prototype type checker based on Typed Racket, which is able to type check many Clojure idioms
  \item We describe a novel use of \emph{occurrence typing} for eliminating occurrences of Java's \emph{null}
  \item We show how a combination of occurrence typing and intersection types allows accurate typing checking of
        the most common usages of Clojure's \emph{sequence abstraction} 
  \item We capture the Clojure idiom of using maps with known keyword fields by using \emph{heterogeneous map types}
  \item We identify the main \emph{future issues} in typing Clojure code.

@@

>>>>

\definecolor{lightorange}{rgb}{0.9,0.4,0}
\definecolor{lightestorange}{rgb}{1,0.8,0.5}
\definecolor{darkorange}{rgb}{0.2,0.1,0}
\definecolor{ForestGreen}{rgb}{0.13, 0.54, 0.13}
\definecolor{navyblue}{rgb}{0,0,0.5}
%%
\begin{poster}%
  % Poster Options
  {
  % Show grid to help with alignment
  grid=false,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lightestorange,
  bgColorTwo=white,
  borderColor=darkorange,
  headerColorOne=ForestGreen,
  headerColorTwo=navyblue,
  headerFontColor=white,
  boxColorOne=green,
  boxColorTwo=blue,
  columns=3,
  % Format of textbox
  textborder=faded,
  % Format of text header
  eyecatcher=true,
  headerborder=closed,
  headerheight=0.1\textheight,
%  textfont=\sc, An example of changing the text font
  headershape=roundedright,
  headershade=shadelr,
  headerfont=\Large\bf\textsc, %Sans Serif
  textfont={\setlength{\parindent}{1.5em}},
  boxshade=plain,
%  background=shade-tb,
  background=none,
  linewidth=2pt
  }
  % Eye Catcher
  {\includegraphics[height=7em]{images/clojure-logo10.png}} 
  % Title
  {\bf\textsc{A Practical Optional Type System for Clojure}}
  % Authors
  %{\textsc{\{ Brian.Amberg and Thomas.Vetter \}@unibas.ch}}
  { \textsc{Ambrose Bonnaire-Sergeant <abonnairesergeant@gmail.com> (20350292)}
    \\
    \textsc{{Supervised by Rowan Davies <rowan@csse.uwa.edu.au>}}}
  % University logo
  {% The makebox allows the title to flow into the logo, this is a hack because of the L shaped logo.
    \includegraphics[width=14em]{images/UWA_logo.png}
  }
%
%  % Eye Catcher
%  {\includegraphics{images/1000px-UWA_crest}}
%   
%  % Title
%  { \textsc}
%  % Authors
%  % University logo
%  { University of Western Australia }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position 
%%% towards an already declared box. So if you have a box attached to the 
%%% bottom, one to the top and a third one which should be in between, you 
%%% have to specify the top and bottom boxes before you specify the middle 
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We take the lessons learnt from several projects to design \emph{Typed Clojure},
an optional type system for Clojure running on the Java Virtual Machine. 
The main contributions are:
\begin{itemize}
  \item We develop a prototype type checker based on Typed Racket [1], which is able to type check many Clojure idioms
  \item We describe a novel use of \emph{occurrence typing} for eliminating erroneous access to Java's \emph{null} pointer
  \item We show how a combination of occurrence typing and intersection types allows accurate typing checking of
        the most common usages of Clojure's \emph{sequence abstraction} 
  \item We capture the Clojure idiom of using maps with known keyword fields by using \emph{heterogeneous map types}
  \item We identify the main \emph{future issues} in typing Clojure code.

@@

  \textsc{\\\smaller Bachelor of Computer Science Honours (Semester 1, 2012)}
\end{posterbox}
